Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}

### 2022-10-21 paper/Paper.tex
last fixes

    \label{fig:abstracted graph}

@@

\noindent \textbf{Synthesizing verified code from MLTL behavior descriptions.} The truth tables generated by the WEST tool can now serve as input to a recently-published toolchain \cite{dasc-2022}. This newly-enabled workflow would produce encodings of the represented MLTL behavior for the interactive theorem prover ACL2, including automatically generating related properties of general interest such as unambiguousness \cite{DBLP:journals/corr/abs-2205-11707,ACL2-Site,ACL2-Doc}. Next, a proof-generating C code synthesizer \cite{DBLP:journals/corr/abs-2205-11708} based on the Axe tool \cite{DBLP:phd/us/Smith11} generates verified software implementing the behaviors originally described in MLTL. By providing a new front-end for this toolchain, we have now enabled a path to generating provably correct software from validated MLTL formulas describing the desired behaviors of a system. Considering the rising popularity of MLTL for describing such behaviors, we expect this to be a rewarding avenue for future exploration.

>>>>

    \label{fig:abstracted_graph}

@@

\noindent \textbf{Synthesizing verified code from MLTL behavior descriptions.} The truth tables generated by the WEST tool can now serve as input to a recently-published toolchain \cite{dasc-2022}. This newly-enabled workflow would produce encodings of the represented MLTL behavior for the interactive theorem prover ACL2, including automatically generating related properties of general interest such as unambiguousness \cite{DBLP:journals/corr/abs-2205-11707,ACL2-Site,ACL2-Doc}. Next, a synthesis pipeline consisting of a verified program transformation suite \cite{Kestrel-APT} along with a proof-generating C code generator \cite{DBLP:journals/corr/abs-2205-11708} (both built on ACL2) generates verified software implementing the behaviors originally described in MLTL.
%a proof-generating C code synthesizer \cite{DBLP:journals/corr/abs-2205-11708} based on the Axe tool \cite{DBLP:phd/us/Smith11} generates verified software implementing the behaviors originally described in MLTL.
By providing a new front-end for this toolchain, we have now enabled a path to generating provably correct software from validated MLTL formulas describing the desired behaviors of a system. Considering the rising popularity of MLTL for describing such behaviors, we expect this to be a rewarding avenue for future exploration.
